\thetitle

### 2021-04-30 writing/rational-stuff.tex
uniform editorial voice, mistakes, typos, size of text in figures, captions
Use configuration consistently in lattice definitions

Applying a mutator to module $\component^*$ of $\system$ acts like a homomorphism
on the generated lattice. The two lattices differ only in the mutated
$\component^*$. Given this formulation, debugging scenarios are those points in
this new lattice that do not contain the mutated module; at all other points, the type
checker points out the type-level mistake in the mutated $\component^*$.

The actions of the rational programmer create an ascending chain---dubbed a
\emph{trail}---in $\lattice{\system}$.  The starting scenario $\conf_0$ of a
trail---also referred to as the \emph{root} (of the trail)---is the initial
debugging scenario.  Starting from such a root, the rational
programmer steps along a trail. If the (program for this) scenario type-checks,
the rational programmer runs the program until it raises a run-time error.  The rational programmer
uses the information in the error to decide which module to equip with
types. This choice constructs scenario $\conf_{i+1}$ from $\conf_{i}$ and thus
creates a trail. The trail's construction ends when it reaches a scenario that
contains the mutated module because the type checker rejects its typed version
outright.  At this point, the source of the impedance mismatch is identified.

>>>>

Applying a mutator to module $\component^*$ of $\system$ acts like a homomorphism
on the generated lattice. The two lattices differ only in the mutated
$\component^*$. Given this formulation, debugging scenarios are those configurations in
this new lattice that do not contain the mutated module; at all other configurations, the type
checker points out the type-level mistake in the mutated $\component^*$.

The actions of the rational programmer create an ascending chain---dubbed a
\emph{trail}---in $\lattice{\system}$.  The {\em root\/} $\conf_0$ of a trail is
the initial debugging scenario.  Starting from such a root, the rational
programmer steps along a trail. If the (program for this) scenario type-checks,
the rational programmer runs the program until it raises a run-time error.  The
rational programmer uses the information in the error to decide which module to
equip with types. This choice constructs scenario $\conf_{i+1}$ from $\conf_{i}$
and thus creates a trail. The trail's construction ends when it reaches a
scenario that contains the mutated module because the type checker rejects its
typed version outright.  At this point, the source of the impedance mismatch is
identified.
